\renewcommand\bibname{Ашигласан материал}
\addcontentsline{toc}{part}{НОМ ЗҮЙ}
\begin{thebibliography}{99}
	\bibitem{nist19}
	NIST Special Database 19
	\\\url{https://www.nist.gov/srd/nist-special-database-19}

	\bibitem{emnist}
	Cohen, G., Afshar, S., Tapson, J., \& van Schaik, A. (2017).
	\\\textit{EMNIST: an extension of MNIST to handwritten letters.}
	\\\url{http://arxiv.org/abs/1702.05373}

	\bibitem{mnist}
	MNIST --- {W}ikipedia{,} The Free Encyclopedia
	\\\url{https://en.wikipedia.org/wiki/MNIST_database}

	\bibitem{mnist-paper}
	Y. Lecun, L. Bottou, Y. Bengio and P. Haffner
	\textit{Gradient-based learning applied to document recognition} in Proceedings of the IEEE, vol. 86, no. 11, pp. 2278-2324, Nov. 1998, doi: 10.1109/5.726791.

	\bibitem{lob-corpus}
	S. Johansson, G.N. Leech, H. Goodluck: \textit{Manual of information to accompany the Lancaster-Oslo/Bergen corpus of British English, for use with digital computers.} Department of English, University of Oslo, Oslo, (1978)

	\bibitem{iam-database}
	Marti, U., Bunke, H. \textit{The IAM-database: an English sentence database for offline handwriting recognition.} IJDAR 5, 39–46 (2002). https://doi.org/10.1007/s100320200071

	\bibitem{etl}
	ETLCD --- ETL Character Database
	\\\url{http://etlcdb.db.aist.go.jp/obtaining-etl-character-database}

	\bibitem{image-processing}
	Digital image processing --- {W}ikipedia{,} The Free Encyclopedia
	\\\url{https://en.wikipedia.org/wiki/Digital_image_processing}

	\bibitem{opencv}
	Bradski, G. (2000). The OpenCV Library. Dr. Dobb's Journal of Software Tools.
	\\\url{https://opencv.org/}

	\bibitem{python}
	Van Rossum, G., Drake Jr, F. L. (2009). \textit{Python 3 Reference Manual. Scotts Valley,} CA: CreateSpace.
	\\\url{http://www.python.org}


\end{thebibliography}
